A New Hybrid Machine Learning Method for Stellar Parameter Inference

### 2025-03-05 paper/paper2/paper.tex
More revisions [78/81]

\begin{abstract}
    The advent of machine learning (ML) is revolutionary to numerous scientific disciplines, with a growing number of examples in astronomical spectroscopic inference, as ML is expected to be more powerful than traditional techniques.
    Here we introduce a hybrid ML (HML) method combin{ing} automatic differentiation, interpolation, and Bayesian optimization to infer stellar parameters given stellar spectra.
    We study $T_{\mathrm{eff}}$, $\log(g)$, and [Fe/H], but this method \textbf{could be extended} to other \textbf{parameters} such as [$\alpha$/Fe] \textbf{(alpha element abundance)}, C/O \textbf{(carbon-oxygen ratio)}, and $f_{sed}$ \textbf{(sedimentation efficiency)}.
    We first use \texttt{blase}'s nontraditional semi-empirical approach, \textbf{recasting} spectra \textbf{into} sets of tunable spectral lines.
    \texttt{blase} is \textbf{run} on 1,314 spectra from \textbf{a rectilinear subset of} the PHOENIX synthetic spectral model grid \textbf{([Fe/H]: [-0.5, 0] dex, $T_\text{eff}$: [2300, 12000] K, $\log(g)$: [2, 6], $\lambda$: [8038, 12849] \AA)}.
    For each of the \textbf{128,723} lines, we continuously map stellar parameters to spectral line parameters using regular grid linear interpolation.
    These manifolds are aggregated to create the PHOENIX generator, \textbf{enabling} parallelized reconstruction of spectra given stellar parameters.
    Gaussian Process minimization is then used to infer stellar parameters by minimizing the root-mean-square (RMS) loss between input and PHOENIX generator spectra.
    From testing, the inference error in $T_{\mathrm{eff}}$ was 185 K, $\log(g)$ was 0.19, and [Fe/H] was 0.12 dex.
    Our products are an archive of the \texttt{blase} \textbf{models} of the PHOENIX subset, as well as the spectral reconstruction and inference algorithms themselves.
    This study is a proof of concept showing that semi-empirical HML is a viable alternative to traditional approaches.
\end{abstract}

@@

\subsection{Line Identification with \texttt{blase}}
The next step was to convert the PHOENIX subset into a physically interpretable intermediate representation: a table of spectral line properties rather than a\textbf{n} array of fluxes.
We used \texttt{blase}, which models spectral lines as Voigt profiles and tunes the profiles to mimic the original PHOENIX spectrum with back propagation.
Back propagation, put simply, is the process of moving in the autodiff gradient field to update ML model parameters (like mentioned earlier, usually against the gradient because we minimize loss functions).
Four parameters were optimized: the line center $\mu$, the log-amplitude $\ln(a)$, the Gaussian width $\sigma$, and the Lorentzian width $\gamma$.
The optimization used the Adam optimizer \textbf{\citep{adam}} with a learning rate of 0.05 over 100 epochs.
\textbf{\citealt{blase} recommends this setup as the minimum, and for a proof-of-concept implementation, we found it best to leave it as is.}
In addition, we limited two custom parameters: wing cut to 6,000 and prominence to 0.005.
Wing cut \textbf{(in pixels)} is a parameter that determines the extent of the Voigt profile to evaluate, saving computational resources by not evaluating negligible line wings.
Prominence \textbf{(in normalized flux counts)} sets a lower limit for the amplitude of detected lines, which saves resources by disregarding shallow lines, so in our case we disregard lines \textbf{with amplitude} $<$ 0.05.
In short, our choices for wing cut and prominence decrease the computational cost of \texttt{blase}'s cloning process at the expense of decreasing its accuracy slightly.
\texttt{blase} uses the pseudo-Voigt approximation, which saves on computational cost while remaining accurate to about 1\% \citep{pseudovoigt}.
The pseudo-Voigt approximation uses a weighted average of a Gaussian and Lorentzian as opposed to a convolution.
\texttt{blase}'s pseudo-Voigt profile implementation uses the following:
\begin{linenomath*}
\begin{subequations}
\begin{gather}
    \tilde{\mathsf{V}}_\mu(\lambda) = a\left[\eta \mathbf{L}(\lambda - \mu'; f) + (1 - \eta)\mathbf{G}(\lambda - \mu'; f)\right]\\
    \eta = \sum_{n=1}^3 \mathbf{u}_n\left(\dfrac{2\gamma}{f}\right)^n\\
    f = 32\sum_{n=0}^5 \mathbf{v}_n \left(\sqrt{2\ln(2)}\sigma\right)^{5-n}(\gamma)^n\\
    \nonumber \mathbf{u} = \mqty[1.36603 \\ -0.47719 \\ 0.11116] \quad \mathbf{v} = \mqty[1 \\ 2.69269 \\ 2.42843 \\ 4.47163 \\ 0.07842 \\ 1]
    \label{eq:equation2}
\end{gather}
\end{subequations}
\end{linenomath*}
where $\mathbf{L}$ and $\mathbf{G}$ are abbreviations for Lorentzian and Gaussian profiles, respectively.
Notice that we use $\mu'$ instead of $\mu$ in the formula.
This is because \texttt{blase} optionally allows the line center to shift slightly during optimization, and it is this shifted center which is used in computation.
The individual Voigt profiles are still indexed by $\mu$ for cross-model line identification, explained in the next section.
Once optimization was complete, the list of identified lines was saved to a `state dictionary': a common representation for pre-trained machine learning models that can be stored to disk for reuse later.
These are stored in the \texttt{.pt} file format for each of the 1,314 PHOENIX subset grid points.
The total disk space these files take up is 465 MB (382 MB when downloaded as a zip archive).
For reference, the storage space the PHOENIX subset takes up on disk is approximately 8.1 GB.
This represents a data compression factor of around 20 just by recasting the spectrum with \texttt{blase}.
\textbf{The state dictionaries are available on Zenodo at \url{https://zenodo.org/records/11246174} \citep{zenodo}.}

@@

Examples of the appearance of missing sections in heatmaps where a line does not appear \textbf{can be seen} in \autoref{fig:figure3} and \autoref{fig:figure4}\textbf{, which show heatmaps of the 11617.66\AA \ C I and the 10123.66\AA \ He II lines \citep{NIST} varying over a solar metallicity slice of the PHOENIX subset stellar parameter space}.
Across the entire PHOENIX subset, \texttt{blase} detected 128,723 spectral lines \textbf{with unique $\mu$}.
\textbf{On average, a PHOENIX spectrum has 9,167 detected spectral lines, with the minimum being 252 ($T_\text{eff}$ = 12,000, $\log(g)$ = 6, [Fe/H] = -0.5) and the maximum being 34,551 ($T_\text{eff}$ = 2,300, $\log(g)$ = 3, [Fe/H] = 0).}
Every one of these lines can be visualized as a manifold mapping a 3D stellar parameter vector to a 4D spectral line parameter vector, and every one \textbf{was} interpolated \textbf{to map stellar parameters to spectral line properties}.
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figure3}
    \caption{Heatmap\textbf{s} showing how $\ln(a)$, $\sigma$\textbf{, $\gamma$, and $\mu' - \mu$} vary over the PHOENIX subset slice at solar metallicity of a \textbf{C I} spectral line.
    Notice the missing chunk in the top left; \textbf{this could perhaps be due to the line center shifting to the point that \texttt{blase} identified the chunk as a different line entirely (notice the line center offset increasing in magnitude approaching the chunk border).}
    \textbf{Since} \texttt{blase} did not detect a spectral line here, \textbf{so} we artificially populate those points with lines that have $\ln(a) = -1000$ \textbf{during interpolation}.
    This and all spectral lines shown in this paper were identified using the NIST spectral line database \citep{NIST}.}
    \label{fig:figure3}
\end{figure*}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figure4}
    \caption{Heatmap showing how $\ln(a)$ and $\sigma$ vary over the PHOENIX subset slice at solar metallicity of a He II spectral line.
    \textbf{This plot is much smaller than \autoref{fig:figure3} because} \texttt{blase} detects this line at a select chunk of grid points, leading to \textbf{data only existing between $T_\text{eff}$ 3600 K and 6600 K}.}
    \label{fig:figure4}
\end{figure}

@@

Finally, the state dictionary is fed into \texttt{blase}'s \texttt{SparseLinearEmulator}, which reconstructs the spectrum by constructing a forward model based on the input state dictionary.
Any \texttt{nan} values are set to 1 (which we can do because the spectra are all normalized), and the spectral reconstruction is complete.
We can observe in \autoref{fig:figure5} that \textbf{a Fe I line from a} reconstructed solar spectrum is not simply a pixel interpolation between the nearest \textbf{PHOENIX} grid point \textbf{spectra}.
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figure5}
    \caption{Plot of an Fe I spectral line shown at the closest PHOENIX grid points to the Sun's stellar parameters \textbf{(solid lines)}, as well as a solar spectrum reconstructed with the PHOENIX generator \textbf{(dotted line)}.
    We can see the spectral line shape be reconstructed mostly between the two native PHOENIX spectra, being closer to the 5800 K spectrum as the Sun's $T_{\mathrm{eff}}$ used here is 5772 K.}
    \label{fig:figure5}
\end{figure*}
It is interpolating the spectral line properties using hundreds of thousands of manifolds, each representing a nonlinear parameter in the shape of the spectral line.

\subsection{Spectral Reconstruction Time}
A typical use case for the PHOENIX generator may be to batch reconstruct spectra from an array of input stellar parameters.
Therefore, there is some motivation to reduce the computational cost of this procedure to tractable levels.
We evaluate the computational time needed to use the PHOENIX generator in two distinct ways.
First, for a single input, which would be relevant in serial applications.
Second, for an array of multiple inputs, which would be relevant in parallel applications.
\textbf{\texttt{scipy}'s} \texttt{RegularGridInterpolator} API allows for the passing in of an entire array of input coordinates to be evaluated at once.
However using \texttt{blase} to reconstruct the spectrum from our interpolated state dictionary is always done serially, leading to what is actually more of a pseudo-parallel evaluation, but extremely performant nonetheless.
Performance results are shown in \autoref{fig:figure6}, and we can see that the multi-reconstruction is much faster than a series of single reconstructions.
\textbf{While the generator takes around 15 seconds per spectrum serially, this drops to 1 second per spectrum as soon as 30 reconstructions.
The speedup factor between the two methods increases as more spectra are generated, reaching a factor of 20 at 60 reconstructions.
The computer used for this test has specifications shown in \autoref{tab:table2} (note that spectral reconstruction does not currently leverage the GPU):}
\begin{table}[h!]
    \centering
    \begin{tabular}{ll}
        \hline
        CPU & AMD EPYC 7513 (32c/64t, 3.65 GHz boost)\\
        RAM & 256 GB\\
        GPU & Nvidia A100 40GB ($\times$2)\\
        \hline
    \end{tabular}
    \caption{\textbf{Specifications of the} machine used for computations, but not for generating visualizations.}
    \label{tab:table2}
\end{table}

\begin{figure}[t!]
    \centering
    \includegraphics[width=\columnwidth]{figure6}
    \caption{\textbf{Plots} showing the time taken to reconstruct varying numbers of spectra using the PHOENIX generator (lower is better).
    We can see that the time taken per spectr\textbf{um} for the serial implementation hovers around 15 seconds within run-to-run variance, while the pseudo-parallel implementation continually decreases in time taken per spectrum as the number of inputs increases.
    The speedup factor (higher is better) increases as more spectra are generated, which is also a desirable outcome.}
    \label{fig:figure6}
\end{figure}

@@

\section{Conclusion}
In this study, we have presented a proof-of-concept algorithm that \textbf{deals with} a subset of the PHOENIX spectral model grid \textbf{([Fe/H]: [-0.5, 0] dex, $T_\text{eff}$: [2300, 12000] K, $\log(g)$: [2, 6], $\lambda$: [8038, 12849] \AA)}.
We create state dictionaries for all spectra in the PHOENIX subset \textbf{using \texttt{blase}, recasting spectra into lists of Voigt profiles, and} lossily compress \textbf{the spectral data by a} factor of around 20. 
The\textbf{y are available on} Zenodo at \url{https://zenodo.org/records/11246174} \citep{zenodo}.
We create the PHOENIX generator and implement a performant spectral reconstruction algorithm, enabling anyone to create reconstructions of PHOENIX spectra with continuously valued stellar parameters.
We introduce and test our \textbf{GP minimization} algorithm \textbf{to infer stellar parameters}, with average absolute deviations from true values of 185 K in $T_\mathrm{eff}$, 0.19 in $\log(g)$, and 0.12 dex in [Fe/H].
In its current state, our algorithm operates on spectra within the PHOENIX subset parameter ranges in \autoref{tab:table1}, requiring that the spectra not contain noticeable Doppler shifting, rotational broadening, or other confounding factors.
The methods discussed here represent a step down a road not traveled in spectral inference, and have the potential to become more advanced in the future by fully utilizing the strengths of physics-informed machine learning.

>>>>

\begin{abstract}
    The advent of machine learning (ML) is revolutionary to numerous scientific disciplines, with a growing number of examples in astronomical spectroscopic inference, as ML is expected to be more powerful than traditional techniques.
    Here we introduce a hybrid ML (HML) method combin{ing} automatic differentiation, interpolation, and Bayesian optimization to infer stellar parameters given stellar spectra.
    We study $T_{\mathrm{eff}}$, $\log(g)$, and [Fe/H], but this method \textbf{could be extended} to other \textbf{parameters} such as [$\alpha$/Fe] \textbf{(alpha element abundance)}, C/O \textbf{(carbon-oxygen ratio)}, and $f_{sed}$ \textbf{(sedimentation efficiency)}.
    We first use \texttt{blase}'s nontraditional semi-empirical approach, \textbf{recasting} spectra \textbf{into} sets of tunable spectral lines.
    \texttt{blase} is \textbf{run} on 1,314 spectra from \textbf{a rectilinear subset of} the PHOENIX synthetic spectral model grid \textbf{($T_\text{eff}$: [2300, 12000] K, $\log(g)$: [2, 6], [Fe/H]: [-0.5, 0] dex, $\lambda$: [8038, 12849] \AA)}.
    For \textbf{128,723 detected features}, we map stellar parameters to spectral line parameters using linear interpolation.
    These manifolds are aggregated to create the PHOENIX generator, \textbf{enabling} parallelized reconstruction of spectra given stellar parameters.
    Gaussian Process minimization is then used to infer stellar parameters by minimizing the root-mean-square loss between input and PHOENIX generator spectra.
    \textbf{In} testing \textbf{210 noise-free synthetic models ($T_{\mathrm{eff}}$: [3000, 11000] K, $\log(g)$: [2, 6], [Fe/H]: [-0.5, 0] dex), we find inference errors of:} $T_{\mathrm{eff}}$\textbf{:} 185 K, $\log(g)$\textbf{:} 0.19, and [Fe/H]\textbf{:} 0.12 dex.
    \textbf{We also publish online} an archive of the \texttt{blase} \textbf{models} of the PHOENIX subset.
    This study is a proof of concept showing that semi-empirical HML is a viable alternative to traditional approaches.
\end{abstract}

@@

\subsection{Line Identification with \texttt{blase}}
The next step was to convert the PHOENIX subset into a physically interpretable intermediate representation: a table of spectral line properties rather than a\textbf{n} array of fluxes.
We used \texttt{blase}, which models spectral lines as Voigt profiles and tunes the profiles to mimic the original PHOENIX spectrum with back propagation.
Back propagation, put simply, is the process of moving in the autodiff gradient field to update ML model parameters (like mentioned earlier, usually against the gradient because we minimize loss functions).
Four parameters were optimized: the line center $\mu$, the log-amplitude $\ln(a)$, the Gaussian width $\sigma$, and the Lorentzian width $\gamma$.
The optimization used the Adam optimizer \textbf{\citep{adam}} with a learning rate of 0.05 over 100 epochs.
\textbf{\citealt{blase} recommends this setup as the minimum, and for a proof-of-concept implementation, we found it best to leave it as is.}
In addition, we limited two custom parameters: wing cut to 6,000 and prominence to 0.005.
Wing cut \textbf{(in pixels)} is a parameter that determines the extent of the Voigt profile to evaluate, saving computational resources by not evaluating negligible line wings.
Prominence \textbf{(in normalized flux counts)} sets a lower limit for the amplitude of detected lines, which saves resources by disregarding shallow lines, so in our case we disregard lines \textbf{with amplitude less than} 0.005.
In short, our choices for wing cut and prominence decrease the computational cost of \texttt{blase}'s cloning process at the expense of decreasing its accuracy slightly.
\texttt{blase} uses the pseudo-Voigt approximation, which saves on computational cost while remaining accurate to about 1\% \citep{pseudovoigt}.
The pseudo-Voigt approximation uses a weighted average of a Gaussian and Lorentzian as opposed to a convolution.
\texttt{blase}'s pseudo-Voigt profile implementation uses the following:
\begin{linenomath*}
\begin{subequations}
\begin{gather}
    \tilde{\mathsf{V}}_\mu(\lambda) = a\left[\eta \mathbf{L}(\lambda - \mu'; f) + (1 - \eta)\mathbf{G}(\lambda - \mu'; f)\right]\\
    \eta = \sum_{n=1}^3 \mathbf{u}_n\left(\dfrac{2\gamma}{f}\right)^n\\
    f = 32\sum_{n=0}^5 \mathbf{v}_n \left(\sqrt{2\ln(2)}\sigma\right)^{5-n}(\gamma)^n\\
    \nonumber \mathbf{u} = \mqty[1.36603 \\ -0.47719 \\ 0.11116] \quad \mathbf{v} = \mqty[1 \\ 2.69269 \\ 2.42843 \\ 4.47163 \\ 0.07842 \\ 1]
    \label{eq:equation2}
\end{gather}
\end{subequations}
\end{linenomath*}
where $\mathbf{L}$ and $\mathbf{G}$ are abbreviations for Lorentzian and Gaussian profiles, respectively.
Notice that we use $\mu'$ instead of $\mu$ in the formula.
This is because \texttt{blase} optionally allows the line center to shift slightly during optimization, and it is this shifted center which is used in computation.
The individual Voigt profiles are still indexed by $\mu$ for cross-model line identification, explained in the next section.
Once optimization was complete, the list of identified lines was saved to a `state dictionary': a common representation for pre-trained machine learning models that can be stored to disk for reuse later.
These are stored in the \texttt{.pt} file format for each of the 1,314 PHOENIX subset grid points.
The total disk space these files take up is 465 MB (382 MB when downloaded as a zip archive).
For reference, the storage space the PHOENIX subset takes up on disk is approximately 8.1 GB.
This represents a data compression factor of around 20 just by recasting the spectrum with \texttt{blase}.
\textbf{The state dictionaries are available on Zenodo at \url{https://zenodo.org/records/11246174} \citep{zenodo}.}

@@

Examples of the appearance of missing sections in heatmaps where a line does not appear \textbf{can be seen} in \autoref{fig:figure3} and \autoref{fig:figure4}\textbf{, which show heatmaps of the 11617.66\AA \ C I and the 10123.66\AA \ He II lines \citep{NIST} varying over a solar metallicity slice of the PHOENIX subset stellar parameter space}.
Across the entire PHOENIX subset, \texttt{blase} detected 128,723 spectral lines \textbf{with unique $\mu$}.
\textbf{On average, a PHOENIX spectrum has 9,167 detected spectral lines, with the minimum being 252 ($T_\text{eff}$ = 12,000, $\log(g)$ = 6, [Fe/H] = -0.5) and the maximum being 34,551 ($T_\text{eff}$ = 2,300, $\log(g)$ = 3, [Fe/H] = 0).}
Every one of these lines can be visualized as a manifold mapping a 3D stellar parameter vector to a 4D spectral line parameter vector, and every one \textbf{was} interpolated \textbf{to map stellar parameters to spectral line properties}.
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figure3}
    \caption{Heatmap\textbf{s} showing how $\ln(a)$, $\sigma$\textbf{, $\gamma$, and $\mu' - \mu$} vary over the PHOENIX subset slice at solar metallicity of a \textbf{C I} spectral line\textbf{, notable for being detected at nearly all subset grid points}.
    Notice the missing chunk in the top left; \textbf{this could perhaps be due to the line center shifting to the point that \texttt{blase} identified the chunk as a different line entirely (notice the line center offset increasing in magnitude approaching the chunk border).}
    \textbf{Since} \texttt{blase} did not detect a spectral line here, we artificially populate those points with lines that have $\ln(a) = -1000$ \textbf{during interpolation}.
    This and all spectral lines shown in this paper were identified using the NIST spectral line database \citep{NIST}.}
    \label{fig:figure3}
\end{figure*}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figure4}
    \caption{Heatmap\textbf{s} showing how $\ln(a)$, $\sigma$\textbf{, $\gamma$, and $\mu' - \mu$} vary over the PHOENIX subset slice at solar metallicity of a He II spectral line.
    \textbf{This plot is much smaller than \autoref{fig:figure3} because} \texttt{blase} detects this line at a select chunk of grid points, leading to \textbf{data only existing between $T_\text{eff}$ 3600 K and 6600 K}.}
    \label{fig:figure4}
\end{figure}

@@

Finally, the state dictionary is fed into \texttt{blase}'s \texttt{SparseLinearEmulator}, which reconstructs the spectrum by constructing a forward model based on the input state dictionary.
Any \texttt{nan} values are set to 1 (which we can do because the spectra are all normalized), and the spectral reconstruction is complete.
\textbf{In \autoref{fig:figure5}, we see a comparison between a PHOENIX generator solar spectrum and two nearby native PHOENIX grid point spectra.}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figure5}
    \caption{Plot of \textbf{the 10123.66 \AA \ He II} spectral line shown at the closest PHOENIX grid points to the Sun's stellar parameters \textbf{(solid lines)}, as well as a solar spectrum reconstructed with the PHOENIX generator \textbf{(dotted line)}.
    We can see the spectral line shape be reconstructed mostly between the two native PHOENIX spectra.}
    \label{fig:figure5}
\end{figure}

We can observe in \autoref{fig:figure6} that \textbf{a Fe I line from a} reconstructed solar spectrum is not simply a pixel interpolation between the nearest \textbf{PHOENIX} grid point \textbf{spectra}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figure6}
    \caption{\textbf{Comparison between the PHOENIX generator's line interpolation and a standard pixel intrpolation of the 10123.66 \AA \ He II spectral line.}}
    \label{fig:figure6}
\end{figure}
It is interpolating the spectral line properties using hundreds of thousands of manifolds, each representing a nonlinear parameter in the shape of the spectral line.

\subsection{Spectral Reconstruction Time}
A typical use case for the PHOENIX generator may be to batch reconstruct spectra from an array of input stellar parameters.
Therefore, there is some motivation to reduce the computational cost of this procedure to tractable levels.
We evaluate the computational time needed to use the PHOENIX generator in two distinct ways.
First, for a single input, which would be relevant in serial applications.
Second, for an array of multiple inputs, which would be relevant in parallel applications.
\textbf{\texttt{scipy}'s} \texttt{RegularGridInterpolator} API allows for the passing in of an entire array of input coordinates to be evaluated at once.
However using \texttt{blase} to reconstruct the spectrum from our interpolated state dictionary is always done serially, leading to what is actually more of a pseudo-parallel evaluation, but extremely performant nonetheless.

Performance results are shown in \autoref{fig:figure7}, and we can see that \textbf{the PHOENIX generator's parallel mode} is much faster than \textbf{serial mode}.
\textbf{While the generator takes around 15 seconds per spectrum in serial mode, this drops to 1 second per spectrum in parallel mode as soon as 30 reconstructions.
The speedup factor between the two methods increases as more spectra are generated, reaching a factor of 20 at 60 reconstructions.
Assuming linear time scaling with wavelength range, according to KORG benchmarks \citep{korg}, which generate spectra over a 500 \AA \ wavelength range, the PHOENIX generator in serial mode is approximately as fast as KORG and $\sim$30 times faster than Turbospectrum \citep{turbospectrum}.
The speedup factor in parallel mode compared to KORG is then the same speedup factor from the serial mode.}

\textbf{The computer used for this test has specifications shown in \autoref{tab:table2} (note that spectral reconstruction does not currently leverage the GPU):}
\begin{table}[h!]
    \centering
    \begin{tabular}{ll}
        \hline
        CPU & AMD EPYC 7513 (32c/64t, 3.65 GHz boost)\\
        RAM & 256 GB\\
        GPU & Nvidia A100 40GB ($\times$2)\\
        \hline
    \end{tabular}
    \caption{\textbf{Specifications of the} machine used for computation.
    \textbf{This machine is owned by Caroline Morley.}}
    \label{tab:table2}
\end{table}

\begin{figure}[t!]
    \centering
    \includegraphics[width=\columnwidth]{figure7}
    \caption{\textbf{Plots} showing the time taken to reconstruct varying numbers of spectra using the PHOENIX generator (lower is better).
    We can see that the time taken per spectr\textbf{um} for the serial implementation hovers around 15 seconds within run-to-run variance, while the pseudo-parallel implementation continually decreases in time taken per spectrum as the number of inputs increases.
    The speedup factor (higher is better) increases as more spectra are generated, which is also a desirable outcome.}
    \label{fig:figure7}
\end{figure}

@@

\section{Conclusion}
In this study, we have presented a proof-of-concept algorithm that \textbf{deals with} a subset of the PHOENIX spectral model grid \textbf{([Fe/H]: [-0.5, 0] dex, $T_\text{eff}$: [2300, 12000] K, $\log(g)$: [2, 6], $\lambda$: [8038, 12849] \AA)}.
We create state dictionaries for all spectra in the PHOENIX subset \textbf{using \texttt{blase}, recasting spectra into lists of Voigt profiles, and} lossily compress \textbf{the spectral data by a} factor of around 20. 
The\textbf{y are available on} Zenodo at \url{https://zenodo.org/records/11246174} \citep{zenodo}.
We create the PHOENIX generator and implement a performant spectral reconstruction algorithm, enabling anyone to create reconstructions of PHOENIX spectra with continuously valued stellar parameters.
We introduce and test our \textbf{GP minimization} algorithm \textbf{to infer stellar parameters.} 
\textbf{Testing on 210 noise-free synthetic models ($T_{\mathrm{eff}}$: [3000, 11000] K, $\log(g)$: [2, 6], [Fe/H]: [-0.5, 0] dex) yields} average absolute deviations from true values of 185 K in $T_\mathrm{eff}$, 0.19 in $\log(g)$, and 0.12 dex in [Fe/H].
In its current state, our algorithm operates on spectra within the PHOENIX subset parameter ranges in \autoref{tab:table1}, requiring that the spectra not contain noticeable Doppler shifting, rotational broadening, or other confounding factors.
The methods discussed here represent a step down a road not traveled in spectral inference, and have the potential to become more advanced in the future by fully utilizing the strengths of physics-informed machine learning.
